---
title: 'Boxcox Stim: Figures for the paper (original SI)'
author: "Gabrielle Boucher"
date: "2025-03-14"
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: united
    number_sections: true
    toc_float: true
    code_folding: "hide"
---



```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE,fig.dim=c(6,6), position = "center", fig.align = 'center')
library(kableExtra)
#library(DT) # for interactive tables
library(readxl)  ## install.packages("tidyverse")
library(openxlsx)
options(stringsAsFactors=FALSE)
library(MASS)
library(psych)
library(lme4) # package for mixed models

windowsFonts(Arial1 ="Arial")

Width1 = 4
height1 = 4
dateOut <- "20250314"
```



```{r}

# boxcox function (I added a default value of 0.5)
bc <- function(x,l=0.5){if(l==0) return(log(x)) else return((x^l-1)/l)}
# inverse boxcox function
ibc <- function(x,l=0.5){if(l==0) return(exp(x)) else return((x*l+1)^(1/l))}

# to be noted; the box-cox is an estimation of log as lambda ->0, for values around 1
# unlike log, it can be computed for 0 (when lambda +0)
# most definition exclude x=0 because of the log case 

# for x=0 values, the box-cox will give: -1/lambda
# this is somehow equivalent to replacing 0s with exp(-1/lambda) in a log transformation
# eg at lambda = 0.5,  this is equivalent to replacing 0s with 0.14
# at lambda = 0.2, this is equivalent to replace 0s with 0.007

# One can do BOTH, ie you can add an epsilon before computing the box cox

# at lambda =1, boxcox is a linear transformation. We then have bc(x1,1) - bc(x0,1) = x1-x0
# If we get the inverse value from this, we get: x1-x0 +1
# the difference is then translated by 1

CV <- function(V) return(sd(V, na.rm=TRUE)/mean(V, na.rm=TRUE))

```



# SI definition

We use here the final proposed SI:

Let’s consider $s_i>0$ and $u_i>0$ to be the stimulated and unstimulated values for a given sample i. We will consider the stimulation index (SI) to be the version with correction:

\begin{equation}
  {{SI}_i=g}_{\lambda}\left(s_i,u_i\right) =
    \begin{cases}
      \left(s_i^\lambda-u_i^\lambda+1-\theta(\lambda) \right)^\frac{1}{\lambda} &, 0 \le \lambda \leq 1 \\
      \  \  \  \  \ \cfrac{s_i}{u_i} &, \lambda = 0.
    \end{cases}       
\end{equation}

Where:
\begin{equation}
  \theta(\lambda) =
    \begin{cases}
      1-(1-\lambda)^{\frac{\lambda}{1-\lambda}} &, \lambda < 0.5  \\
      \lambda^{\frac{1-\lambda}{\lambda}} &,  \lambda \geq 0.5  \\
    \end{cases}       
\end{equation}



```{r}

SI <- function(x1,x0,L=0.5,H=NULL, s=1, e=0,OOB.V=1E-3, corrected=FALSE){
 
  # The function can be applied to vectors or matrix
  # x0 is unstim
  # x1 is stim
  
  # L is lambda
  # H is  Theta for correcting of the translation issue
  # You can set H as you wish, e.g set to 0 for small lambda and set to 1 for lambda close to 1
  # corrected =TRUE set a H value by default, which is F1(L) (see below)
 
  # setting H cancels the "corrected" option
  
  # OOB.V can be set to a low value, such as 1E-3
  # It can also be set to NaN or NA
  # This is the value returned when the SI is not defined; due to unstim >> stim
  
  # e and s are scaling factors. By default: no scaling
  
  
  F1 <- function(L){
    # S shaped function for the correction
    # returns 1 when L=1, 0 when L=0, 0.5 when L=0.5
    # with and S shape to get quick convergence to 0 and 1
    
    sign0 <- function(v){
      sg <- sign(v)
      sg[s==0] <- 1
      return(sg)
    } 
    
    L0 <- abs(L-0.5)+0.5
    f1 <- L0^((1-L0)/L0)
    
    f1 <- sign0(L-0.5)*f1 +(-sign0(L-0.5) +1)/2
    
    return(f1)
  }
  
  
  d <- dim(x1)  # will be NULL if single value or vector, else will be nrow, ncol
  if(!is.null(d)) if(sum(dim(x0) != d)>0) stop("x0 and x1 not the same dimension\n")
  
  #scaling
  x1 <- unlist((x1-e)/s)
  x0 <- unlist((x0-e)/s)
  if(length(x0) != length(x1)) stop("x0 and x1 not the same length\n")
  
  if(!is.null(H) & corrected){ corrected <- FALSE; warning("corrected set to FALSE\n")}

  if(corrected){
    H <- F1(L)
  }
  if(is.null(H)) H <- 0
  
  res <- NA*x1
  if(L>0 & L<=1){
    OOB <- which((x1^L+1-H)^(1/L) < x0 )   # out of bound (exclude NAs)
    N.OOB <- which((x1^L+1-H)^(1/L) >= x0 )   # not out of bound (exclude NAs)
    res[N.OOB] <- (x1[N.OOB]^L-x0[N.OOB]^L+1-H)^(1/L)
    res[OOB] <- OOB.V
  }
  if(L==0) res <- x1/x0
  
  dim(res) <- d
  return(res)
}


```



 
# test on dataset

We are using here the dataset including repeats from different centers. "ring testing"

In this version, we use correction=FALSE, to get the original SI, that is $\theta =0$ .



```{r}
load(file = "../Stim_Unstim_20230417/Processed_data_20230526.Rdata")
Param = names(DAT_CMV.o)[5:14]
Param <- Param[-c(1,2,7)]
Param2 <- Param
Param2 <- gsub("p", "+", Param2, fixed = TRUE)
Param2 <- gsub("_", " ", Param2, fixed = TRUE)
Param2 <- gsub("CD107a", "CD107a+", Param2, fixed = TRUE)
Param2 <- gsub("++", "+", Param2, fixed = TRUE)

colsite <- c("gray50", "purple", "orange")[as.numeric(as.factor(DAT_CMV.o.all$Site))]
Leg1 <- unique(data.frame(Site=DAT_CMV.o.all$Site, col=colsite))

Leg1

epsilon <- 1E-3
LL <- seq(0,1,0.01)



```


We will use mixed models and the ratio of variances to evaluate effects of transformation. The ratio of between sample variance to total variance is equivalent to ICC2.

The ratio illustrated in plots were originaly:

black: subj/total
red: Site/Total
orange: Experiment/Total
blue: Error /Total

But here we use only Subj/total, in green.


```{r}
plot.su <- function(MyPar){
  plot(DAT_Unstim.o.all[[Param[MyPar]]],DAT_CMV.o.all[[Param[MyPar]]],
     col=colsite,
     xlab="unstim", ylab="CMV", main=Param2[MyPar])
}
```


```{r}
plot.su.log <- function(MyPar){
  plot(log2(DAT_Unstim.o.all[[Param[MyPar]]]+epsilon),log2(DAT_CMV.o.all[[Param[MyPar]]]+epsilon),
     col=colsite,
     xlab="unstim (log2)", ylab="CMV (log2)", main=Param2[MyPar])
}
```


```{r}
getstats1 <- function(MyPar){

wnana <- which( is.na(DAT_CMV.o.all[[Param[MyPar]]]) | is.na(DAT_Unstim.o.all[[Param[MyPar]]]))

DAT2 <- data.frame(value=DAT_CMV.o.all[[Param[MyPar]]] +epsilon, Subj=DAT_CMV.o.all$SampleID, Site=DAT_CMV.o.all$Site, Exp=paste0(DAT_CMV.o.all$Site,DAT_CMV.o.all$Experiment))
DAT2$value[wnana] <- NA

LM2 <- lmer(value~(1|Site) + (1|Exp)+ (1|Subj), data=DAT2)

print(summary(LM2)) # print the variances

# variance components
VSite <- VarCorr(LM2)$Site[1,1]
VExp <- VarCorr(LM2)$Exp[1,1]
VSubj <- VarCorr(LM2)$Subj[1,1]
V_Error <- attributes(VarCorr(LM2))$sc^2

CV1 <- median(aggregate(DAT2$value,by=list(DAT2$Subj), CV)$x)
return(data.frame(LL=NA,VSite,VExp,VSubj,V_Error, V_total=NA,Median.CV=CV1))
}
```



```{r}
getstats1.log <- function(MyPar){

wnana <- which( is.na(DAT_CMV.o.all[[Param[MyPar]]]) | is.na(DAT_Unstim.o.all[[Param[MyPar]]]))

DAT2 <- data.frame(value=DAT_CMV.o.all[[Param[MyPar]]] +epsilon, Subj=DAT_CMV.o.all$SampleID, Site=DAT_CMV.o.all$Site, Exp=paste0(DAT_CMV.o.all$Site,DAT_CMV.o.all$Experiment))
DAT2$value[wnana] <- NA

LM2 <- lmer(log2(value+epsilon)~(1|Site) + (1|Exp)+ (1|Subj), data=DAT2)

print(summary(LM2)) # print the variances

# variance components
VSite <- VarCorr(LM2)$Site[1,1]
VExp <- VarCorr(LM2)$Exp[1,1]
VSubj <- VarCorr(LM2)$Subj[1,1]
V_Error <- attributes(VarCorr(LM2))$sc^2

CV1 <- median(aggregate(DAT2$value,by=list(DAT2$Subj), CV)$x)
return(data.frame(LL=NA,VSite,VExp,VSubj,V_Error, V_total=NA,Median.CV=CV1))
}
```


```{r}

getstats.L <- function(MyPar, RES1){
MyVar <- data.frame(LL)
MyVar$VSite=NA
MyVar$VExp=NA
MyVar$VSubj=NA
MyVar$V_Error = NA
MyVar$V_total = NA
MyVar$Median.CV <- NA

MyVar <- rbind(MyVar, RES1)

wnana <- which( is.na(DAT_CMV.o.all[[Param[MyPar]]]) | is.na(DAT_Unstim.o.all[[Param[MyPar]]]))


for(k in 1:length(LL)){

DAT2 <- data.frame(value=SI(DAT_CMV.o.all[[Param[MyPar]]]+epsilon,DAT_Unstim.o.all[[Param[MyPar]]]+epsilon, LL[k]), Subj=DAT_CMV.o.all$SampleID, Site=DAT_CMV.o.all$Site, Exp=paste0(DAT_CMV.o.all$Site,DAT_CMV.o.all$Experiment))
DAT2$value[wnana] <- NA

LM2 <- lmer(value~(1|Site) + (1|Exp)+ (1|Subj), data=DAT2)

#summary(LM2) # get the variances
#if(LL[k]==0.5) Mod.0.5 <- LM2

# variance components
MyVar$VSite[k] <- VarCorr(LM2)$Site[1,1]
MyVar$VExp[k]  <- VarCorr(LM2)$Exp[1,1]
MyVar$VSubj[k]  <- VarCorr(LM2)$Subj[1,1]
MyVar$V_Error[k]  <- attributes(VarCorr(LM2))$sc^2

MyVar$Median.CV[k] <- mean(aggregate(DAT2$value,by=list(DAT2$Subj), CV)$x)
}

MyVar$V_total <- with(MyVar,VSite +  VExp + VSubj + V_Error)
MyVar$Ratio.Subj <- with(MyVar,VSubj/V_total)
MyVar$Ratio.Site <- with(MyVar,VSite/V_total)
MyVar$Ratio.Exp <- with(MyVar,VExp/V_total)
MyVar$Ratio.Error <- with(MyVar,V_Error/V_total)

return(MyVar)
}

```



```{r}

getstats.L.log <- function(MyPar, RES1){
MyVar <- data.frame(LL)
MyVar$VSite=NA
MyVar$VExp=NA
MyVar$VSubj=NA
MyVar$V_Error = NA
MyVar$V_total = NA
MyVar$Median.CV <- NA

MyVar <- rbind(MyVar, RES1)

wnana <- which( is.na(DAT_CMV.o.all[[Param[MyPar]]]) | is.na(DAT_Unstim.o.all[[Param[MyPar]]]))


for(k in 1:length(LL)){

DAT2 <- data.frame(value=SI(DAT_CMV.o.all[[Param[MyPar]]]+epsilon,DAT_Unstim.o.all[[Param[MyPar]]]+epsilon, LL[k]), Subj=DAT_CMV.o.all$SampleID, Site=DAT_CMV.o.all$Site, Exp=paste0(DAT_CMV.o.all$Site,DAT_CMV.o.all$Experiment))
DAT2$value[wnana] <- NA

LM2 <- lmer(log2(value+epsilon)~(1|Site) + (1|Exp)+ (1|Subj), data=DAT2)

#summary(LM2) # get the variances
#if(LL[k]==0.5) Mod.0.5 <- LM2

# variance components
MyVar$VSite[k] <- VarCorr(LM2)$Site[1,1]
MyVar$VExp[k]  <- VarCorr(LM2)$Exp[1,1]
MyVar$VSubj[k]  <- VarCorr(LM2)$Subj[1,1]
MyVar$V_Error[k]  <- attributes(VarCorr(LM2))$sc^2

MyVar$Median.CV[k] <- mean(aggregate(DAT2$value,by=list(DAT2$Subj), CV)$x)
}

MyVar$V_total <- with(MyVar,VSite +  VExp + VSubj + V_Error)
MyVar$Ratio.Subj <- with(MyVar,VSubj/V_total)
MyVar$Ratio.Site <- with(MyVar,VSite/V_total)
MyVar$Ratio.Exp <- with(MyVar,VExp/V_total)
MyVar$Ratio.Error <- with(MyVar,V_Error/V_total)

return(MyVar)
}

```



```{r}
plot.LL <- function(MyPar,MyVar){
plot(MyVar$LL, MyVar$Ratio.Subj, type="l", 
     ylim=c(0,1), xlab=expression(lambda),ylab="Variance Ratio (Donor/Total)",
     main=Param2[MyPar], las=1, col="darkgreen")
#lines(MyVar$LL,MyVar$Ratio.Site,col="red")
#lines(MyVar$LL,MyVar$Ratio.Exp,col="orange")
#lines(MyVar$LL,MyVar$Ratio.Error,col="blue")

wraw <- which(is.na(MyVar$LL))
abline(h=MyVar$Ratio.Subj[wraw], col="gray50", lty=2)
#abline(h=MyVar$Ratio.Site[wraw], col="pink", lty=2)
#abline(h=MyVar$Ratio.Exp[wraw], col="goldenrod1", lty=2)
#abline(h=MyVar$Ratio.Error[wraw],col="skyblue", lty=2)

abline(v=LL[which.max(MyVar$Ratio.Subj[-wraw])])
}
```
```{r}
plot.CV <-  function(MyPar,MyVar){
plot(MyVar$LL, MyVar$Median.CV, type="l", 
     ylim=c(0,1), xlab=expression(lambda),ylab="Median CV",
     main=Param2[MyPar], las=1, family="Arial1")
}

```


# Evaluation on original scale

```{r}
MyPar <- 1
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r}
plot.CV(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```






```{r}
MyPar <- 2
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r}
plot.CV(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```





```{r}
MyPar <- 3
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r}
plot.CV(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```




```{r}
MyPar <- 4
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r}
plot.CV(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```



```{r}
MyPar <- 5
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r}
plot.CV(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```




```{r}
MyPar <- 6
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r}
plot.CV(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```





```{r}
MyPar <- 7
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r}
plot.CV(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```


```{r, eval=FALSE}
Y1 <- matrix(DAT2$value[1:18],6,3,byrow=TRUE)
Y2 <- matrix(DAT2$value[19:36],6,3,byrow=TRUE)
Y3 <- matrix(DAT2$value[37:54],6,3,byrow=TRUE)
Y <- cbind(Y1,Y2,Y3)
```


# Evaluation on the Log scale



```{r}
MyPar <- 1
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su.log(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1.log(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L.log(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```





```{r}
MyPar <- 2
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su.log(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1.log(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L.log(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```





```{r}
MyPar <- 3
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su.log(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1.log(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L.log(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```





```{r}
MyPar <- 4
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su.log(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1.log(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L.log(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```




```{r}
MyPar <- 5
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su.log(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1.log(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L.log(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```





```{r}
MyPar <- 6
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su.log(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1.log(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L.log(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```




```{r}
MyPar <- 7
```

## `r Param2[MyPar]`

Lets consider `r Param2[MyPar]`.

If we plot the CMV vs unstim, colored by sites, we get:

```{r}
plot.su.log(MyPar)
```



We can see the correlation between unstim and stim, and the strata from sites.

In a mixed model of the stim data:

```{r}
RES1 <- getstats1.log(MyPar)
```


We can see the variance for sites, vs donors (Subj), experiments and error.


Then, if we correct the stim by unstim, varying $\lambda$:

```{r, include=FALSE}
RES2 <- getstats.L.log(MyPar, RES1)
```

```{r}
plot.LL(MyPar,RES2)
```

```{r, include =FALSE}
pdf(file=paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".pdf"), width=Width1, height=height1)
par(mar=c(4,4,2,2))
plot.LL(MyPar,RES2)
dev.off()
write.xlsx(RES2,paste0("Boxcox_ICC_log_", Param[MyPar], "_original_", dateOut, ".xlsx"))
```



